Proofs of Linearizability Based on Forward Simulations

### 2017-01-25 draftCAV/stack.tex
small things

\vspace{-3mm}
\subsection{Abstract stack implementation}
\vspace{-1mm}
We define an abstract stack $AbsS$ over alphabet $C\cup R\cup Com(pop)$ that essentially, similarly to $AbsQ$, maintains the happens-before order of the push operations whose value has not been yet removed. Pop operations are treated differently since the commit points are not necessarily linearization points. Intuitively, each pop operation starts by taking a snapshot of the greatest completed push operations in the happens-before order, and continuously tracks the push operations which are overlapping with it. The commit point $com(pop,d,k)$ with $d\neq {\tt EMPTY}$ is enabled only if $d$ was added by one of the push operations in the initial snapshot, or by a push happening earlier when all the values from the initial snapshot have been removed, or by one of the push operations that overlaps with pop $k$. The commit point $com(pop,{\tt EMPTY},k)$ is enabled only if all the values added by push operations ending before $k$ started have been removed. The effect of the commit points is explained below through examples.
\vspace{-.4mm}

>>>>

\vspace{-3mm}
\subsection{Abstract stack implementation}
\vspace{-1mm}
We define an abstract stack $AbsS$ over alphabet $C\cup R\cup Com(pop)$ that essentially, similarly to $AbsQ$, maintains the happens-before order of the pushes whose value has not been yet removed. Pops are treated differently since the commit points are not necessarily linearization points, intuitively, a pop can be linearized before its commit. Each pop operation starts by taking a snapshot of the greatest completed push operations in the happens-before order, and continuously tracks the push operations which are overlapping with it. The commit point $com(pop,d,k)$ with $d\neq {\tt EMPTY}$ is enabled only if $d$ was added by one of the push operations in the initial snapshot, or by a push happening earlier when all the values from the initial snapshot have been removed, or by one of the push operations that overlaps with pop $k$. The commit point $com(pop,{\tt EMPTY},k)$ is enabled only if all the values added by push operations ending before $k$ started have been removed. The effect of the commit points is explained below through examples.
\vspace{-.4mm}
